Vulnerability Analysis of Container Images in Neuroimaging

### 2020-07-17 paper.tex
content fix 1

\journal{gigascience}

%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{csvsimple}
\usepackage{minted} % Used for JSON highlighting
\usepackage{datatool}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{array}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage{anyfontsize}
\usepackage[flushleft]{threeparttable}

@@

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}
\begin{filecontents*}{resul.csv}
labels,names,A,C,V,Stools
a,bids/example:latest,838,663,683,
b,bids/freesurfer:latest,353,215,192,
c,bids/ndmg:latest,934,757,782,
d,\textcolor{red}{bids/broccoli:v1.0.0},79,79,117,
e,bids/fibredensityandcrosssection:latest,1086,849,868,
f,bids/spm:latest,191,246,235,
g,poldracklab/mriqc:0.15.0,432,328,332,
h,bids/cpac:v1.0.1a\_22,698,524,535,
I,bids/hyperalignment:latest,1717,1327,1433,
j,bids/mindboggle:0.0.4-1,671,955,569,
k,bids/mrtrix3\_connectome:latest,275,157,158,
l,bids/rs\_signal\_extract:0.1,867,454,473,
m,bids/aa:v0.2.0,189,244,233,
n,bids/niak:latest,1482,1366,1420,
o,bids/oppni:v0.7.0-1,913,698,723,
p,poldracklab/fmriprep:unstable,516,355,393,
q,bids/brainiak-srm:latest,897,484,503,
r,bids/nipypelines:0.3.0,641,878,451,
s,bids/hcppipelines:v3.17.0-18,526,873,620,
t,bids/magetbrain:latest,112,117,126,
u,bids/tracula:v6.0.0-4,874,664,683,
v,bids/baracus:latest,172,238,216,
w,bids/antscorticalthickness:v2.2.0-1,289,27,no OVAL data,
x,bids/dparsf:v4.3.12,507,750,757,
y,bids/afni\_proc:latest,67,16,no OVAL data,
z,bids/rshrf:1.0.1,5,3,3,
aa,bids/ndmg:v0.1.0,934,758,782,
ab,\textcolor{red}{mcin/qeeg:latest},46,46,142,
ac,\textcolor{red}{camarasu/creaphase:0.3},54,54,186,
ad,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
ae,\textcolor{red}{mcin/docker-fsl:latest},75,75,201,
af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
ag,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
ah,\textcolor{red}{bt5e/ants:latest},150,156,336,
ai,poldracklab/fmriprep:1.2.3,591,441,447,
aj,gkiar/dwipreproc\_fsl-5.0.11\_minified:latest,391,258,263,
ak,gkiar/mask2boundary:v0.1.0,15,11,11,
al,\textcolor{red}{mcin/ica-aroma:latest},75,75,202,
am,c3genomics/genpipes,,,,99
an,bioinformatics-group/aqua-singularity-recipe,,,,7
ao,MontrealSergiy/BEst,,,,106
ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
aq,shots47s/bids-freesurfer-6.0,,,,212
ar,shots47s/bids-fmriprep-1.2.3,,,,453
\end{filecontents*}

@@

\affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}

\maketitle

@@

Today, containers, which provide operating system level virtualization, are
popular. Correspondingly, they are widely used for scientific data analyses on 
High Performance Computing (HPC) clusters. However, the security of containers
still remains a concerning issue. Here, we focus on the security of container
images, which are often built for the entire
duration of an analysis, so scientific researchers prefer not to update
them. Consequently, their chances of containing vulnerabilities increases.  
In this study, we analyze vulnerabilities in container images used in 
HPC clusters.
We conduct two different
experiments, image update and image minimization, to report the effect 
on the number of vulnerabilities.

@@

\textit{RQ1: What is the current amount of known vulnerabilities in
container images deployed on HPC clusters?} Vulnerabilities are possible
attack vectors that may seriously compromise the security of HPC clusters
and the integrity of user data. We report vulnerability analyses produced
by four popular image scanning tools, Anchore, Vuls, Clair-scanner and Stools.

@@

The next section describes the materials and tools used in the experiments,
including image scanners and container images. We then describe our image
update and minimization methodology to reduce vulnerabilities. Results review
the detected vulnerabilities in container images, explain observed
discrepancies between scanners, and report on the efficiency of image
update and size reduction. As a conclusion, we provide a set of image
creation guidelines for a secure deployment on HPC clusters.

%This paper is organized as follows: in the next section, we provide a description
%of materials and methods which summarize our experiments. We also explain different
%image scanners used to report
%vulnerabilities in container images. The next section of this paper provides the results, where we
%present a number of existing vulnerabilities in the container images
%used for data analysis on shared HPC clusters. We then proceed in the following section with 
%discussion and analysis of these results, where we provide more insight into the problems that 
%we faced while conducting these experiments. We also propose some
%particular rules that can be followed to secure container images. Finally, conclusions are drawn
%in the last section of the paper.

%%%%%%%%%Related Work%%%%%%%
The existing research work on containers focuses mainly on the security of containers.
This focus is justified by the fact that containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis}.
Other work studied security vulnerabilities on Docker hub. A study in 2015 by Gummaraju et al.
states that over 30\% of official images in docker hub contain high priority 
security vulnerabilities~\cite{gummaraju2015over}. Shu et al. show that both official and community images 
contain more than 180 vulnerabilities on an average~\cite{Shu2017}.
Zerouali et al. studied that 
outdated packages lead to bugs and severity vulnerabilities in Docker
images~\cite{zerouali2019relation}.

@@

Since the aim of this research work is to detect security vulnerabilities
in container images and attempt to examine the effect of different
manipulation of these images, it is needed to have a representative set of
images. Additionally, for the purpose of detecting vulnerabilities,
utilization of image scanners is required. We utilize container
images from two popular application frameworks, as well as
four of the main image scanners.

@@

We scan a total of 44 container images taken from two containerization frameworks
used in neuroscience: BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}.
Out of these 44 images, 26 were obtained from BIDS apps
(\url{https://bids-apps.neuroimaging.io/apps/}) 
and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
out of which one wasn't available on DockerHub. Boutiques had 49 images, listed using
Boutiques \texttt{bosh search} command,
however, only 23 unique images were listed, out of which 3 couldn't be retrieved and 2
were already included in BIDS apps. All the final 26 images
from BIDS apps are Docker images, whereas Boutiques contains 18 Docker images
and 6 Singularity images.

@@

We use four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair~\cite{arminc_2019} and
Singularity Container Tools --- Stools~\cite{stools}. Anchore, Vuls and Clair support Docker
images while Stools support Singularity. Different vulnerabilities may be
reported if scanning experiments take place on different dates.
To avoid such discrepancies, we freeze the vulnerability
databases used by these scanners as of 2019-09-25, when we initiate our
experiments. This allows for a fair comparison between the scanners.

@@

Anchore is an end-to-end, open-source container security platform. It
analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
In our experiments, we use Anchore Engine version 0.5.0 through Docker image \texttt{anchore/anchore-engine:v0.5.0}, and
Anchore vulnerability database version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources. The Table~\ref{database} displays a list of all sources
that it refers at the time of this study.

%for instance, Ubuntu launchpad database to get
%vulnerability data related to Ubuntu

%\begin{figure*}[!ht]
%    \centering
%	\begin{subfigure}[t]{0.3\textwidth}
%        \includegraphics[height=2.0in]{Figures/anchore.png}
%        \caption{Anchore}
%        \label{anchore}
%    \end{subfigure}%
%    ~ 
%	\begin{subfigure}[t]{0.3\textwidth}
%        \includegraphics[height=2.5in]{Figures/vuls.png}
%        \caption{Vuls}
%        \label{vuls}
%    \end{subfigure}
%     ~
%	\begin{subfigure}[t]{0.3\textwidth}
%        \includegraphics[height=2.0in]{Figures/clair.png}
%        \caption{Clair}
%	\label{clair}
%    \end{subfigure}
%    \caption{Vulnerability databases used by scanners}
%    \label{database}
%\end{figure*}
\begin{figure*}
\begin{tabular}{ |c|c|c|c| }
 \hline
\textbf{OS} &	\textbf{Anchore} &	\textbf{Vuls} &	\textbf{Clair} \\
\hline
	\textbf{Alpine} & Alpine-SecDB &	Alpine-SecDB &	Alpine-SecDB \\
\hline
	\textbf{CentOS} & Red Hat Enterprise Linux Oval & Red Hat Enterprise Linux OVAL And Red Hat Security Advisories & Red Hat Security Data \\
\hline
	\textbf{Debian} & Debian Security Bug Tracker &	Debian OVAL and Debian Security Bug Tracker & Debian Security Bug Tracker \\
\hline
	\textbf{Ubuntu} & Ubuntu CVE Tracker &	Ubuntu OVAL &	Ubuntu CVE Tracker \\
 \hline
\end{tabular}
\caption{Vulnerability databases used by scanners for different OS distributions}
\label{database}
\end{figure*}

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
starts a container for every image to test, and queries the package manager
in the image through SSH. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources, which are listed in the Table~\ref{database}.
%from the Open Vulnerability
%and Assessment Language (OVAL) database 
According to this list, Vuls
refers to Open Vulnerability and Assessment Language (OVAL) database for some distribution e.g. Ubuntu, Debian, etc.
It is worth noting that there is
no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
with these distributions cannot be scanned with Vuls.

@@

Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
vulnerability scanner for Docker and appc container images, developed by
CoreOS (now Container Linux), a Linux distribution to deploy container
clusters. Clair has a client-server architecture, in which the server
scans Docker images layer by layer and maintains a database of vulnerabilities. We use Clair through Clair-scanner
(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
of container images against a local Clair server. Clair-scanner scans the image,
prepares the list of vulnerabilities, compares that list against a
whitelist, and flags vulnerabilities that are not present in the whitelist.
In our experiments, we did not use a whitelist to filter scanning results in
order to make a fair comparison between scanners.
Clair scanner maintains a Docker image with the up-to-date vulnerability
database from a set of different sources listed in the Table~\ref{database}.
We use Clair-scanner version 2.0.6, executed through
Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
database, we use Docker image \texttt{arminc/clair-db:latest}, last
updated on 2019-09-18.

@@

Singularity Tools (Stools)
are an extension of Clair scanner for Singularity images. Stools
exports Singularity image to \texttt{tar.gz} format, masquerading as a single layer docker image
to circumvent the Docker-specific requirements in the Clair API.
In our experiments, we use Singularity Tools version 3.2.1 through Docker
image
\texttt{vanessa/stools-clair:v3.2.1}, which is using another Docker
image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
We follow the steps mentioned in
\href{https://github.com/singularityhub/stools}{Stools Github} to scan
Singularity images.

@@

BIDS apps and Boutiques images in our experiments have diverse Linux
distributions, such as Ubuntu, CentOS, Debian, and Alpine. A particular
distribution has different releases in general. Regarding Ubuntu, it has different
types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
differently depending on the different Ubuntu release types. It is 
important to provide an overview of these Ubuntu releases types, 
since Ubuntu is heavily utilized in our experiments. 
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
to LTS release only while collecting data from the vulnerability databases.
More interestingly, scanners are able to refer to ESM release vulnerability database
even without purchase, however, this may lead to discrepancies in results.
%If scanners refer to ESM release for 
%vulnerability data, it may lead to discrepancies in results.
Further, if an image is using a Linux release where EOL has been reached that image may
turns to be vulnerable as it is not possible to retrieve any updates.
%Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
%resulting in vulnerable images.

@@

\begin{figure}[!ht]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
\end{figure}

%\begin{figure*} \centering{
%\includegraphics{status.pdf}}
%\caption{Experiment 1}
%\end{figure*}

%\includegraphics[width=300, max width=\textwidth]{status.pdf}

%\begin{table*}[!ht]
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\textwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c | c | c | c| c | c},
%	table head =Image Labels & {Image names} & {Anchore} & {Clair} & {Vuls} &{Stools} & {a} & {b} & {c} & {d}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{status.csv}{}{\csvlinetotablerow}%
%       \centering
%        \caption{\label{status}Number of vulnerabilities by scanners}
%\end{table*}

\section{Reducing the amount of vulnerabilities}

In this section, we present our approach to reduce the number of
vulnerabilities in container images  by updating and minimizing these
images.

\subsection{Image Update Process}

If vulnerabilities exist in the container images, then our first approach
is to update these images in order to see the effects of such updates
on the vulnerabilities.
Updating an image involves updating all software packages that are
inside that image. We use a 
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{bash script} 
to update all images. That script checks the
package manager, which is present inside the image, and updates the image
accordingly. However, this action affects the reproducibility
of that image. For example, if a package is used in an experiment
and later that package is updated, subsequent instances of the experiment may actually
get different results.
%which means that the image cannot be used to verify the research
%findings of other scientists.

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, an open-source tool that
helps scientists to make their research reproducible. This tool traces operating system calls used by the
application during execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

>>>>

\journal{gigascience}
%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{csvsimple}
\usepackage{minted} % Used for JSON highlighting
\usepackage{datatool}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{array}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage{anyfontsize}
\usepackage[flushleft]{threeparttable}

@@

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}
\begin{filecontents*}{resul.csv}
labels,names,A,C,V,Stools
a,bids/example:latest,838,663,683,
b,bids/freesurfer:latest,353,215,192,
c,bids/ndmg:latest,934,757,782,
d,\textbf{bids/broccoli:v1.0.0},79,79,117,
e,bids/fibredensityandcrosssection:latest,1086,849,868,
f,bids/spm:latest,191,246,235,
g,poldracklab/mriqc:0.15.0,432,328,332,
h,bids/cpac:v1.0.1a\_22,698,524,535,
I,bids/hyperalignment:latest,1717,1327,1433,
j,bids/mindboggle:0.0.4-1,671,955,569,
k,bids/mrtrix3\_connectome:latest,275,157,158,
l,bids/rs\_signal\_extract:0.1,867,454,473,
m,bids/aa:v0.2.0,189,244,233,
n,bids/niak:latest,1482,1366,1420,
o,bids/oppni:v0.7.0-1,913,698,723,
p,poldracklab/fmriprep:unstable,516,355,393,
q,bids/brainiak-srm:latest,897,484,503,
r,bids/nipypelines:0.3.0,641,878,451,
s,bids/hcppipelines:v3.17.0-18,526,873,620,
t,bids/magetbrain:latest,112,117,126,
u,bids/tracula:v6.0.0-4,874,664,683,
v,bids/baracus:latest,172,238,216,
w,bids/antscorticalthickness:v2.2.0-1,289,27,no OVAL data,
x,bids/dparsf:v4.3.12,507,750,757,
y,bids/afni\_proc:latest,67,16,no OVAL data,
z,bids/rshrf:1.0.1,5,3,3,
aa,bids/ndmg:v0.1.0,934,758,782,
ab,\textbf{mcin/qeeg:latest},46,46,142,
ac,\textbf{camarasu/creaphase:0.3},54,54,186,
ad,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
ae,\textbf{mcin/docker-fsl:latest},75,75,201,
af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
ag,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
ah,\textbf{bt5e/ants:latest},150,156,336,
ai,poldracklab/fmriprep:1.2.3,591,441,447,
aj,gkiar/dwipreproc\_fsl-5.0.11\_minified:latest,391,258,263,
ak,gkiar/mask2boundary:v0.1.0,15,11,11,
al,\textbf{mcin/ica-aroma:latest},75,75,202,
am,c3genomics/genpipes,,,,99
an,bioinformatics-group/aqua-singularity-recipe,,,,7
ao,MontrealSergiy/BEst,,,,106
ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
aq,shots47s/bids-freesurfer-6.0,,,,212
ar,shots47s/bids-fmriprep-1.2.3,,,,453
\end{filecontents*}

@@

\affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}
\maketitle

@@

Today, containers, which provide operating-system level virtualization, are
popular. Correspondingly, they are widely used for scientific data analyses on 
High Performance Computing (HPC) clusters. However, the security of containers
still remains a concerning issue. Here, we focus on the security of container
images, which are often built for the entire
duration of an analysis, so scientific researchers prefer not to update
them. Consequently, their chances of containing vulnerabilities increases.  
In this study, we analyze vulnerabilities in container images used in 
HPC clusters.
We conduct two different
experiments, image update and image minimization, to report the effect 
on the number of vulnerabilities.

@@

\textit{RQ1: What is the current amount of known vulnerabilities in
container images deployed on HPC clusters?} Vulnerabilities are possible
attack vectors that may seriously compromise the security of HPC clusters
and the integrity of user data. We report vulnerability analyses produced
by four popular image scanning tools, Anchore, Vuls, Clair, and Stools.

@@

The next section describes the materials and tools used in the experiments,
including container images and image scanners. We then describe our image
update and minimization methodology to reduce vulnerabilities. Results review
the detected vulnerabilities in container images, explain observed
discrepancies between scanners, and report on the efficiency of image
update and size reduction. As a conclusion, we provide a set of image
creation guidelines for a secure deployment on HPC clusters.

The existing research work on containers focuses mainly on the security of containers.
This focus is justified by the fact that containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis}.
Other work studied security vulnerabilities in Docker images. A study in 2015 by Gummaraju et al.
states that over 30\% of official images in docker hub contain high priority 
security vulnerabilities~\cite{gummaraju2015over}. Shu et al. show that both official and community images 
contain more than 180 vulnerabilities on an average~\cite{Shu2017}.
Zerouali et al. studied that 
outdated packages lead to bugs and severity vulnerabilities in Docker
images~\cite{zerouali2019relation}.

@@

Since the aim of this research work is to detect security vulnerabilities
in container images and attempt to examine the effect of different
manipulations on these images, it is needed to have a representative set of
images. Additionally, for the purpose of detecting vulnerabilities,
utilization of image scanners is required. We utilize container
images from two popular application frameworks, as well as
four of the main image scanners.

@@

We scan all container images, available at the time of this study, on two containerization frameworks
used in neuroscience: BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}, totalling
44 container images.
Out of these 44 images, 26 were obtained from BIDS apps
(\url{https://bids-apps.neuroimaging.io/apps/}) 
and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
out of which one wasn't available on DockerHub. Boutiques had 49 images,
%listed using Boutiques \texttt{bosh search} command,
however, only 23 unique images were listed, out of which 3 couldn't be retrieved and 2
were already included in BIDS apps. All the final 26 images
from BIDS apps are Docker images, whereas Boutiques contains 18 Docker images
and 6 Singularity images.

@@

We use four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair~\cite{arminc_2019} and
Singularity Container Tools --- Stools~\cite{stools}. Anchore, Vuls and Clair support Docker
images while Stools support Singularity. Different vulnerabilities may be
reported by scanners if scanning experiments take place on different dates.
To avoid such discrepancies, we freeze the vulnerability
databases used by these scanners as of 2019-09-25, when we initiate our
experiments. This allows for a fair comparison between the scanners.

@@

Anchore is an end-to-end, open-source container security platform. It
analyze	container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
In our experiments, we use Anchore Engine version 0.5.0 through Docker image \texttt{anchore/anchore-engine:v0.5.0}, and
Anchore vulnerability database version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources. Table~\ref{database} displays Anchore's vulnerability sources for
Ubuntu, Debian, Alpine, and Centos, which are present inside taken images.
Anchore also refers to National
Vulnerability Database (NVD) to get metadata of vulnerabilities.

\begin{figure*}
\begin{tabular}{ |c|c|c|c| }
 \hline
\textbf{OS} &	\textbf{Anchore} &	\textbf{Vuls} &	\textbf{Clair} \\
\hline
	\textbf{Alpine} & Alpine-SecDB &	Alpine-SecDB &	Alpine-SecDB \\
\hline
	\textbf{CentOS} & Red Hat Enterprise Linux Oval & Red Hat Enterprise Linux OVAL And Red Hat Security Advisories & Red Hat Security Data \\
\hline
	\textbf{Debian} & Debian Security Bug Tracker &	Debian OVAL and Debian Security Bug Tracker & Debian Security Bug Tracker \\
\hline
	\textbf{Ubuntu} & Ubuntu CVE Tracker &	Ubuntu OVAL &	Ubuntu CVE Tracker \\
 \hline
\end{tabular}
\caption{Vulnerability databases used by scanners for different OS distributions}
\label{database}
\end{figure*}

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
connects to the running containers that needs to be scanned through SSH, and queries the package manager
in the container. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:0.9.0}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources. Table~\ref{database} lists vulnerability databases
referred by Vuls for scanned four OS distributions i.e. Alpine, Ubuntu, Debian, and Centos.
Apart from this, like Anchore, Vuls also refers NVD database for getting vulnerability metadata.
Table~\ref{database} shows that Vuls
refers to Open Vulnerability and Assessment Language (OVAL) database for Ubuntu, Debian, and Centos.
It is worth noting that there is
no vulnerability data for Ubuntu 17.04 and 17.10 distributions in OVAL database, meaning that images
with these distributions cannot be scanned with Vuls.

@@

Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
vulnerability scanner for Docker and appc container images, developed by
CoreOS (now Container Linux), a Linux distribution to deploy container
clusters. Clair has a client-server architecture, in which the server
scans Docker images layer by layer and maintains a database of vulnerabilities. We use Clair through Clair-scanner
(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
of container images against a local Clair server. Clair-scanner scans the image,
prepares a list of vulnerabilities, compares that list against a
whitelist, and flags vulnerabilities that are not present in the whitelist.
In our experiments, we did not use a whitelist to filter scanning results in
order to make a fair comparison between scanners.
Clair-scanner maintains a Docker image with the up-to-date vulnerability
database from a set of different sources. Table~\ref{database} lists
vulnerability databases that Clair referred for Alpine, Ubuntu, Debian, and Centos.
Clair also uses NVD database for getting vulnerability metadata.
We use Clair version 2.0.6, executed through
Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
database, we use Docker image \texttt{arminc/clair-db:latest}, last
updated on 2019-09-18.

@@

Singularity Tools (Stools)
are an extension of Clair for Singularity images. Stools
exports Singularity images to \texttt{tar.gz} format, acting as a single layer Docker image
to circumvent the Docker-specific requirements in the Clair API.
In our experiments, we use Singularity Tools version 3.2.1 through Docker
image
\texttt{vanessa/stools-clair:v3.2.1}, which is using another Docker
image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
Since Stools uses Clair internally for scanning, vulnerability databases used
by Stools are same as mentioned for Clair.
To scan Singularity images, we follow the steps mentioned in
\href{https://github.com/singularityhub/stools}{Stools Github}.

@@

BIDS apps and Boutiques images in our experiments have four Linux
distributions i.e. Ubuntu, CentOS, Debian, and Alpine. A particular
distribution has different releases in general. Regarding Ubuntu, it has different
types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
differently depending on the different Ubuntu release types. It is 
important to provide an overview of these Ubuntu releases types, 
since Ubuntu is heavily utilized in our experiments. 
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
to LTS release only while collecting data from the vulnerability databases.
More interestingly, scanners are able to refer to ESM release vulnerability database
even without purchase, however, this may lead to discrepancies in results.
Further, if an image is using a Linux release where EOL has been reached that image may
turns to be vulnerable as it is not possible to retrieve any updates.

@@

\begin{figure}[!ht]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
\end{figure}
\vspace*{-7mm}
\section{Reducing the amount of vulnerabilities}

In this section, we present our approach to reduce the number of
vulnerabilities in container images  by updating and minimizing these
images.
\vspace*{-2mm}
\subsection{Image Update Process}

If vulnerabilities exist in the container images, then our first approach
is to update these images in order to see the effects of such updates
on the vulnerabilities.
Updating an image involves updating all software packages that are
inside that image. We use a 
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{bash script} 
to update all images. That script checks the
package manager, which is present inside the image, and updates the image
accordingly. However, this action affects the reproducibility
of that image. For example, if a package is used in an experiment
and later that package is updated, subsequent instances of the experiment may actually
get different results.
\vspace*{-2mm}
\subsection{Image Minimization Process}

We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, an open-source tool that
helps scientists to make their research reproducible. This tool traces operating system calls used by the
application during execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

Following the two previous approaches, we employ a hybrid approach, where
we combine both update and size reduction processes in an attempt to
lessen number of vulnerabilities or to test the effect of
combining two approaches. To allow for that, we first update all packages in
the image, then delete all unnecessary packages. Applying these processes in reverse
may reduce the needed work; however this is not possible in all cases. For instance,
some packages, such as \texttt{apt-transport-https}, are required to fetch updates, deleting these packages
ahead of time will disallow the update process to take place.
\vspace*{-2mm}
\section{Results}

In this section,
we first discuss the detected vulnerabilities in the images and compare the
results. We then discuss the effect of updating/minimizing the image and applying the hybrid
approach on the detected vulnerabilities.
Lastly, we do an analysis of obtained results and explain the reasons behind our
findings.
\vspace*{-2mm}
\subsection{Detected Vulnerabilities}
